% autogenerated latex script: Trouble with Diyas
\documentclass{script}

% this sets whether things stretch to the bottom of the page or not
% I figure most teensyville scripts will be cut smaller so don't need to stretch
\setboolean{teensyville}{false}

\begin{document}
\begin{doubledoc}{
\scriptname{Trouble with Diyas}

\begin{chartype}{Townsfolk}
\character{washerwoman}{Washerwoman}{You start knowing that 1 of 2 players is a particular Townsfolk.}
\character{chef}{Chef}{You start knowing how many pairs of evil players there are.}
\character{librarian}{Librarian}{You start knowing that 1 of 2 players is a particular Outsider. (Or that zero are in play.)}
\character{hanuman}{Hanuman}{You start knowing 3 good characters. One is in play, one is a demon bluff and one is not in play. You don't know which is which.}
\character{empath}{Empath}{Each night, you learn how many of your 2 alive neighbours are evil.}
\character{yudhishthir}{Yudhishthir}{You are "mad" that you are Yudhishthir, or else you lose your ability. Each night, choose two players. Learn how many of them are evil.}
\character{undertaker}{Undertaker}{Each night*, you learn which character died by execution today.}
\character{monk}{Monk}{Each night*, choose a player (not yourself): they are safe from the Demon tonight.}
\character{virgin}{Virgin}{The 1st time you are nominated, if the nominator is a Townsfolk, they are executed immediately.}
\character{slayer}{Slayer}{Once per game, during the day, publicly choose a player: if they are the Demon, they die.}
\character{kalki}{Kalki}{If you were killed by the Demon in the night, you come back to life in the night when there are 4 or fewer alive, with a not-in-play townsfolk ability.}
\character{narasimha}{Narasimha}{If Hiranyakashipu is your alive neighbour, they die (not the first night). [+ Hiranyakashipu]}
\character{mayor}{Mayor}{If only 3 players live \& no execution occurs, your team wins. If you die at night, another player might die instead.}
\end{chartype}

\begin{chartype}{Outsiders}
\character{vibhishan}{Vibhishan}{You start as an Evil player. If dead equal or outnumber the living, you switch alignments and become good.}
\character{curseofyayati}{Curse of Yayati}{1 Townsfolk starts unknowingly with the Curse of Yayati. The Curse passes to the person that nominates them. A player with the Curse is Drunk and might register as Evil, minion or demon.}
\character{recluse}{Recluse}{You might register as evil \& as a Minion or Demon, even if dead.}
\character{saint}{Saint}{If you die by execution, your team loses.}
\end{chartype}

\begin{chartype}{Minions}
\character{poisoner}{Poisoner}{Each night, choose a player: they are poisoned tonight and tomorrow day.}
\character{hiranyakashipu}{Hiranyakashipu}{You cannot die by execution. Everyone knows who you are. You keep your eyes open at night. If Narasimha is your alive neighbour, you die.}
\character{scarletwoman}{Scarlet Woman}{If there are 5 or more players alive \& the Demon dies, you become the Demon.}
\character{baron}{Baron}{There are extra Outsiders in play. [+2 Outsiders]}
\end{chartype}

\begin{chartype}{Demons}
\character{shakuni}{Shakuni}{Each night* choose a player, they die. When choosing the player, guess what character the player is. If correct, you get to pick again.}
\character{raavana}{Raavana}{Each night*, choose a player, they die. When receiving bluffs, choose one of them. You gain that ability and may register as good and that character to all Townsfolk abilities.  [+1 Outsider]}
\character{imp}{Imp}{Each night*, choose a player: they die. If you kill yourself this way, a Minion becomes the Imp.}
\end{chartype}

\notfirstnight
}\end{doubledoc}

\newpage

\begin{doubledoc}{

\begin{nights}{
\nighttext{\color{red}M}{Minion Info}
\nighttext{\color{red}D}{Demon Info}
\nighticon{curseofyayati}{Curse of Yayati}
\nighticon{hiranyakashipu}{Hiranyakashipu}
\nighticon{poisoner}{Poisoner}
\nighticon{raavana}{Raavana}
\nighticon{vibhishan}{Vibhishan}
\nighticon{chef}{Chef}
\nighticon{librarian}{Librarian}
\nighticon{washerwoman}{Washerwoman}
\nighticon{hanuman}{Hanuman}
\nighticon{empath}{Empath}
\nighticon{yudhishthir}{Yudhishthir}
}{
\nighticon{hiranyakashipu}{Hiranyakashipu}
\nighticon{poisoner}{Poisoner}
\nighticon{monk}{Monk}
\nighticon{imp}{Imp}
\nighticon{shakuni}{Shakuni}
\nighticon{raavana}{Raavana}
\nighticon{scarletwoman}{Scarlet Woman}
\nighticon{narasimha}{Narasimha}
\nighticon{vibhishan}{Vibhishan}
\nighticon{empath}{Empath}
\nighticon{yudhishthir}{Yudhishthir}
\nighticon{undertaker}{Undertaker}
\nighticon{kalki}{Kalki}
}\end{nights}

}\end{doubledoc}
\end{document}
