% autogenerated latex script: Diyas of Wrath
\documentclass{script}

% this sets whether things stretch to the bottom of the page or not
% I figure most teensyville scripts will be cut smaller so don't need to stretch
\setboolean{teensyville}{false}

\begin{document}
\begin{doubledoc}{
\scriptname{Diyas of Wrath}

\begin{chartype}{Townsfolk}
\character{hanuman}{Hanuman}{You start knowing 3 good characters. One is in play, one is a demon bluff and one is not in play. }
\character{karna}{Karna}{You start knowing 2 good players. Choose one to recieve Kavacha (protected against executions), the other Kundala (protected against the demon).}
\character{drona}{Drona}{You start knowing 1 good player and their character as your student. If they die, you get a new student.}
\character{sita}{Sita}{Pick a consort. Each night, learn which characters picked either you or your consort.}
\character{laxman}{Laxman}{Each night, choose a player (different from last night). They cannot die if both their alive neighbours are good.}
\character{yudhishthir}{Yudhishthir}{Each night, choose 2 players. Learn how many of them are evil. You must be "mad" as Yudhisthir, else you lose this ability.}
\character{krishna}{Krishna}{Each night, learn how long the longest chain of alive good Townsfolk is.}
\character{bhishma}{Bhishma}{Once per game, at night*, choose if you wish to die. Only you die that night.}
\character{savitribai}{Savitribai}{Once per game, at night*, choose a dead player. They are resurrected.}
\character{ram}{Ram}{Any nominations made by you or on you, follow the rules of an exile.}
\character{yama}{Yama}{Once per game, publicly use your ability. That day, only you \& the dead can nominate and vote. A vote token or a majority isn't required.}
\character{ganesh}{Ganesh}{You cannot be executed unless the demon votes for you. You are safe from the demon. If just <= 4 players live, you lose this ability.}
\character{durga}{Durga}{You learn who the demon is. If an executed Demon publicly guesses you (once), evil wins, even if you're dead. [+1 Outsider]}
\character{kalki}{Kalki}{If you were killed by the Demon, you get resurrected on the night with <= 4 players alive, with a not-in-play Townsfolk ability.}
\character{narasimha}{Narasimha}{Each night*, if Hiranyakashipu is your alive neighbour, they die. [+ Hiranyakashipu]}
\end{chartype}

\begin{chartype}{Outsiders}
\character{kaikeyi}{Kaikeyi}{1 good and 1 evil player have their positions swapped in the Grimoire.}
\character{vibhishan}{Vibhishan}{You start as an Evil player. If dead equal or outnumber the living, you become Good.}
\character{ashwathama}{Ashwathama}{On your 1st night, choose 3 players (not yourself); 1 is poisoned, 1 might die at anytime, and 1 is safe from all evil abilities; even if you are dead.}
\character{curseofyayati}{Curse of Yayati}{1 Townsfolk starts unknowingly with the Curse of Yayati. They are drunk and might register as Evil, minion or demon. The Curse passes to whoever nominates them.}
\end{chartype}

\begin{chartype}{Minions}
\character{atanu}{Atanu}{Each night, choose 2 alive players. If they have a private discussion with each other, both are poisoned until dawn.}
\character{shurpanakha}{Shurpanakha}{Each day, if any nomination does not get enough votes, either the nominator or the nominee might die tonight.}
\character{amba}{Amba}{If you die by execution, an alive minion may swap roles with the demon. That night, you kill upto the number of alive evil players.}
\character{hiranyakashipu}{Hiranyakashipu}{You cannot die by execution. Everyone knows who you are. You keep your eyes open at night.}
\end{chartype}

\begin{chartype}{Demons}
\character{raavana}{Raavana}{Each night*, choose a player, they die. Choose one demon bluff, you gain that ability. You may register as good or that character to Townsfolk abilities. [+1 Outsider]}
\character{shakuni}{Shakuni}{Each night* choose a player, they die. If you also correctly guess their character, you get to pick again.}
\character{kumbhakarna}{Kumbhakarna}{Each night*, choose if you wish to wake up or not. For each night you have not woken up in the game, choose a player, they die. }
\character{mahishasura}{Mahishasura}{Each night*, choose a player, they die. You gain all not-in-play Minion abilities until there are <= 4 players alive.}
\end{chartype}

\notfirstnight
}\end{doubledoc}

\newpage

\begin{doubledoc}{

\begin{nights}{
\nighttext{\color{red}M}{Minion Info}
\nighttext{\color{red}D}{Demon Info}
\nighticon{durga}{Durga}
\nighticon{curseofyayati}{Curse of Yayati}
\nighticon{kaikeyi}{Kaikeyi}
\nighticon{hiranyakashipu}{Hiranyakashipu}
\nighticon{sita}{Sita}
\nighticon{raavana}{Raavana}
\nighticon{vibhishan}{Vibhishan}
\nighticon{ashwathama}{Ashwathama}
\nighticon{karna}{Karna}
\nighticon{drona}{Drona}
\nighticon{hanuman}{Hanuman}
\nighticon{laxman}{Laxman}
\nighticon{yudhishthir}{Yudhishthir}
\nighticon{krishna}{Krishna}
\nighticon{atanu}{Atanu}
}{
\nighticon{kaikeyi}{Kaikeyi}
\nighticon{hiranyakashipu}{Hiranyakashipu}
\nighticon{bhishma}{Bhishma}
\nighticon{vibhishan}{Vibhishan}
\nighticon{laxman}{Laxman}
\nighticon{shurpanakha}{Shurpanakha}
\nighticon{raavana}{Raavana}
\nighticon{shakuni}{Shakuni}
\nighticon{kumbhakarna}{Kumbhakarna}
\nighticon{mahishasura}{Mahishasura}
\nighticon{amba}{Amba}
\nighticon{kalki}{Kalki}
\nighticon{ganesh}{Ganesh}
\nighticon{savitribai}{Savitribai}
\nighticon{narasimha}{Narasimha}
\nighticon{yudhishthir}{Yudhishthir}
\nighticon{krishna}{Krishna}
\nighticon{drona}{Drona}
\nighticon{atanu}{Atanu}
\nighticon{sita}{Sita}
}\end{nights}

}\end{doubledoc}
\end{document}
